---
title: "R Notebook"
output:
#  html_notebook: default
  html_document:
    df_print: paged
  word_document: default
---

```{r load_libraries, echo=F}
library(DBI)
library(RPostgreSQL)
library(tibble)
library(dplyr)
library(ggplot2)
library(lubridate)
library(timetk)
library(config)

config <- config::get()
```

```{r set_up_db, echo=F}

pgsqldrv <- dbDriver("PostgreSQL")

con <- dbConnect(pgsqldrv,
  user = config$netsuite$user,
  password = config$netsuite$password,
  dbname = config$netsuite$dbname,
  host = config$netsuite$host
)
```

The below code controls the date range that the analysis is performed over.

```{r set_up_params}
begin_date <- '2018-01-01'
end_date <- '2018-12-31'
```

Retrieve all actual sales information (net of credits):

```{sql sales_query, connection=con, output.var="item_sales_raw"}
WITH sales_info AS (
  SELECT
    nsi.item_id,
    nst.trandate::date AS trandate,
    nstl.item_count * '-1'::integer::numeric AS qty,
    nstl.net_amount * '-1'::integer::numeric AS amount,
    nstl.subsidiary_id,
    nst.sales_order_type_id
  FROM
    netsuite.transaction_lines nstl
    LEFT JOIN netsuite.transactions nst ON nst.transaction_id = nstl.transaction_id
    LEFT JOIN netsuite.items nsi ON nsi.item_id = nstl.item_id
  WHERE (
    nst.transaction_type::text = ANY (ARRAY[
      'Cash Sale'::text,
      'Invoice'::text
    ])
  ) AND (
    nsi.type_name::text = ANY (ARRAY[
      'Non-inventory Item'::character varying::text,
      'Inventory Item'::character varying::text,
      'Assembly/Bill of Materials'::character varying::text,
      'Kit/Package'::character varying::text,
      'Item Group'::character varying::text
    ])
  )
  AND (nst.trandate >= to_date(?begin_date,'YYYY-MM-DD'))
  AND (nst.trandate <= to_date(?end_date,'YYYY-MM-DD'))
)

SELECT
  sales_info.item_id,
  sales_info.trandate,
  sales_info.qty,
  sales_info.amount,
  sales_info.subsidiary_id,
  sales_info.sales_order_type_id
FROM sales_info
```

Retrieve credit information:

```{sql credit_query, connection=con, output.var="item_returns_raw"}
WITH sales_info AS (
  SELECT
    nsi.item_id,
    nst.trandate::date AS trandate,
    nstl.item_count * '-1'::integer::numeric AS qty,
    nstl.net_amount * '-1'::integer::numeric AS amount,
    nstl.subsidiary_id,
    nst.sales_order_type_id
  FROM
    netsuite.transaction_lines nstl
    LEFT JOIN netsuite.transactions nst ON nst.transaction_id = nstl.transaction_id
    LEFT JOIN netsuite.items nsi ON nsi.item_id = nstl.item_id
  WHERE (
    nst.transaction_type::text = ANY (ARRAY[
      'Cash Refund'::text,
      'Credit Memo'::text
    ])
  ) AND (
    nsi.type_name::text = ANY (ARRAY[
      'Non-inventory Item'::character varying::text,
      'Inventory Item'::character varying::text,
      'Assembly/Bill of Materials'::character varying::text,
      'Kit/Package'::character varying::text,
      'Item Group'::character varying::text
    ])
  )
  AND (nst.trandate >= to_date(?begin_date,'YYYY-MM-DD'))
  AND (nst.trandate <= to_date(?end_date,'YYYY-MM-DD'))
)

SELECT
  sales_info.item_id,
  sales_info.trandate,
  sales_info.qty,
  sales_info.amount,
  sales_info.subsidiary_id,
  sales_info.sales_order_type_id
FROM sales_info
```

Retrieve purchase order data

```{sql subsidiary_query, connection=con, output.var="subsidiaries"}
SELECT
  subsidiary_id,
  name
FROM
netsuite.subsidiaries

```

```{r Disconnect From Database}
dbDisconnect(con)
```

Data's retrieved, so it's useful to scrub some known issues. Item groups are in sales and credit data, but the actual posting transactions are against the members of these groups, so we can scrub out anything with an N/A amount.
```{r Filter N/A Values}
item_sales <- item_sales_raw %>% filter(!is.na(amount))
item_returns <- item_returns_raw %>% filter(!is.na(amount))
```

It's useful to glance, at least initially, on some summary statistics to see if they make sense:


```{r Initial Stats}
summary(item_sales$amount)
summary(item_sales$trandate)
```


```{r Change Summary}
sales_by_day <-  item_sales %>%
  group_by(day=floor_date(trandate, "day"), subsidiary_id) %>%
  summarize(amount=sum(amount))

sales_by_week <-  item_sales %>%
  group_by(day=floor_date(trandate, "week"), subsidiary_id) %>%
  summarize(amount=sum(amount))

sales_by_month <- item_sales %>%
  group_by(month=floor_date(trandate, "month"), subsidiary_id) %>%
  summarize(amount=sum(amount))

sales_by_day <- as_tibble(base::merge(sales_by_day, subsidiaries, by="subsidiary_id"))
sales_by_week <- as_tibble(base::merge(sales_by_week, subsidiaries, by="subsidiary_id"))
sales_by_month <- as_tibble(base::merge(sales_by_month, subsidiaries, by="subsidiary_id"))
```

```{r Plot Sales}
# set strings as factors to false
options(stringsAsFactors = FALSE)

sales_by_month %>%
ggplot() +
  geom_line(data = sales_by_week, aes(x = day, y = amount, group=name, color=name)) +
  labs(title = "Sales by Week",
     subtitle = "The data frame is sent to the plot using pipes",
     y = "Dollar Amount",
     x = "Date")
```

```{r}
sales_by_week_can <- sales_by_week %>% filter(subsidiary_id == 3)
sales_by_week_usa <- sales_by_week %>% filter(subsidiary_id == 2)

sales_by_week_can_rel <- sales_by_week_can %>%
  mutate(amountT = sum(amount)) %>%
  mutate(perTotal = amount / amountT)

sales_by_week_usa_rel <- sales_by_week_usa %>%
  mutate(amountT = sum(amount)) %>%
  mutate(perTotal = amount / amountT)
```

```{r}
ggplot() +
  geom_line(data = sales_by_week_can_rel, aes(x = day, y = perTotal, group=name, color=name)) +
  geom_line(data = sales_by_week_usa_rel, aes(x = day, y = perTotal, group=name, color=name)) +
  labs(title = "Percent of Total Sales: By Week",
#     subtitle = "The data frame is sent to the plot using pipes",
     y = "Percent of Total",
     x = "Date")

```